---
title: "MovieLens_Recommendation_Systems "
author: "Joyce Mugisha"
date: "2023-08-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Introduction**  
In a realm dominated by virtual marketplaces, recommendation systems have assumed a pivotal role that used to be carried out by in-person sales staff, driving a company's sales and revenue. Leveraging the power of Machine Learning, the task of processing vast datasets to derive analytical insights and predictions has evolved into a streamlined and efficient process.

In this context, I will illustrate the analytical processing of data using the [MovieLens](https://grouplens.org/datasets/movielens/10m/) through a Machine Learning recommendation system.

## MovieLens 10M dataset:
## https://grouplens.org/datasets/movielens/10m/
## http://files.grouplens.org/datasets/movielens/ml-10m.zip




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
